Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-05 authorinstr_2.tex

\subsection{Twitter API}
\section{Single tweet analysis}
In this section we will discuss the different types of analysis that can be done on one single tweet. This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets. 
\subsection{Data enrichment}
At the very basis of the analysis of a tweet is data enrichment. Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about. To get a better understanding of the meaning of a tweet, a context is needed. For humans this is done by linking the information from the tweet to earlier acquired knowledge. The same thing can be done by computers. 
\subsubsection{Context creation}
The problem of linking tweets to another source of information poses the biggest issue in data enrichment. The tweets themselves do not provide much information. Fortunately, Kwak et al. have shown that the topic of over 85\% of the of the tweets is related to news \cite{newsmedia}. This knowledge can be leveraged to create a context for most of the tweets.  This is what Abel et al. proposed to do\cite{enrichmentForProfiling}. They linked tweets to mainstream news networks like CNN, BBC and New York Times.

@@

>>>>

\subsection{Twitter API}

When Twitter was conceived, the developers decided that to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
beneficial to both Twitter's popularity and alot of its users, including researchers.

An overview of the API structure and some useful fields:
\begin{enumerate}
\item \textbf{Tweets} The short messages sent by users
	\subitem \textbf{Coordinates} Retrieves the longitude and latitude position from where a specified tweet has been sent
	\subitem \textbf{Entities} Retrieves the entities (url, hashtag, etc.) that are embedded into the tweet
	\subitem \textbf{Lang} Retrieves the language in which a tweet has been sent
	\subitem \textbf{User} Retrieves the user that sent a tweet
\item \textbf{Users} The accounts that send tweets
	\subitem \textbf{Description} Retrieves the description that the user defined for his account
	\subitem \textbf{Location} Retrieves the location that the user defined for his account
	\subitem \textbf{Status} Retrieves, if possible, the user's latest tweet
\item \textbf{Entities} Images, hashtags and other entities that tweets can hold
	\subitem \textbf{Hashtags} Retrieves the hashtags that have been parset out of a tweet
	\subitem \textbf{Media} Retrieves the media that is associated with a tweet
	\subitem \textbf{urls} Retrieves the urls embedded in a tweet
	\subitem \textbf{user\_mentions} Retrieves the users that have been mentioned in a tweet
\item \textbf{Places} Predefined places on Twitter that users can associate with
	\subitem \textbf{Country} Retrieves the country associated with a place
	\subitem \textbf{Full\_name} Retrieves the full name of a place, for example Kanses ``City, Kansas''
	\subitem \textbf{Place\_type} Retrieves the type of a place, for example ``city''
\end{enumerate}

When the above fields are combined, it is possible to create sets of Tweets that fulfill a certain specification. These sets can be used to extract information.
No matter how specific you can define your search, sometimes you need a random sample of tweets to analyse. For this purpose, Twitter has a stream that
third party developers can tap into to retrieve random tweets. Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.

The following of this article describes algorithms that dive into the big data of Twitter, how to extract useful information from the tweets, and what the information
can be applied to.

\newpage

\section{Single tweet analysis}
In this section we will discuss the different types of analysis that can be done on one single tweet. This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets. 
\subsection{Data enrichment}
At the very basis of the analysis of a tweet is data enrichment. Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about. To get a better understanding of the meaning of a tweet, a context is needed. For humans this is done by linking the information from the tweet to earlier acquired knowledge. The same thing can be done by computers. 
\subsubsection{Context creation}
The problem of linking tweets to another source of information poses the biggest issue in data enrichment. The tweets themselves do not provide much information. Fortunately, Kwak et al. have shown that the topic of over 85\% of the of the tweets is related to news \cite{newsmedia}. This knowledge can be leveraged to create a context for most of the tweets.  This is what Abel et al. proposed to do\cite{enrichmentForProfiling}. They linked tweets to mainstream news networks like CNN, BBC and New York Times.

@@

\begin{enumerate}
\item \textbf{Linear-Weighted Hybrid}\\

%TODO: Technische stuff begrijpen zodat ik die hier neer kan zetten + bibliography laten doorverwijzen

\item \textbf{Pair-Wise Interaction Tensor Factorization} The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has
been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter.

\end{enumerate}
